Global study of well-being and internet adoption | Online analysis supplement

### 2021-11-15 _lme4-time.Rmd
save lmer code

# Time trends

```{r packages}
#| results: 'hide'
# Packages
library(ggtext)
library(brms)
library(ellipse)
library(broom.mixed)
library(scales)
library(ggh4x)
library(tidybayes)
library(ggdist)
library(parameters)
library(lme4)
library(emmeans)
library(patchwork)
library(bayestestR)
library(lubridate)
library(broom)
library(kableExtra)
library(ggstance)
library(tidyverse)

# MCMC settings
options(brms.backend = "cmdstanr")
hmc <- list(iter = 2250, warmup = 1000, refresh = 50, d = .9)
# Run this to delete fitted models and refit
# unlink(list.files(pattern = "output/brm-.*\\.rds"))
```

## Model 1: Temporal trends

We then model the mental health and well-being outcomes over time allowing for heterogeneity across locations and demographic groups.

We first fit the models using lme4 because they are big and therefore would be very slow with brms.

### GBD

@@

```{r fit-gbd-time-lme4}
# These take about 5-20 minutes each
# run in parallel in background jobs
# recommended to conduct this in interactive mode (rstudio)
file_path <- "output/lme4-gbd-time.rds"
if (!file.exists(file_path)) {
  library(job)
  job({fit_anx <- lmer(
    Anxiety ~ 1 + time * sex * age + 
      (1 + time * sex * age | region) +
      (1 + time * sex * age | country),
    data = gbd_wide
  )}, title = "Anxiety time (lmer)")
  job({fit_dep <- lmer(
    Depression ~ 1 + time * sex * age + 
      (1 + time * sex * age | region) +
      (1 + time * sex * age | country),
    data = gbd_wide
  )}, title = "Depression time (lmer)")
  job({fit_sel <- lmer(
    Selfharm ~ 1 + time * sex * age + 
      (1 + time * sex * age | region) +
      (1 + time * sex * age | country),
    data = gbd_wide
  )}, title = "Self harm time (lmer)")
  fits_lmer <- distinct(gbd, cause) %>% 
    mutate(fit = list(fit_anx, fit_dep, fit_sel))
  write_rds(fits_lmer, file_path)
} else {fits_lmer <- read_rds(file_path)}
```

@@

#### brms

correlating temporal trends in outcomes and internet use using multilevel model with shared correlation matrix

note we use beta so transform edge values

we start with non interactive model--demographics are covariates. later to be expanded to interaction but slow

##### Time: Main effects

We first fit a multivariate model of time effects on internet penetration and each of the well-being outcomes.

$$
\begin{align*}
y_{i[c][r]} &\sim \text{Normal}(\mu^y_{i[c][r]}, \sigma^{2y}) \\

\mu^y_{i[c][r]} &= \beta^{y}_{0} + \gamma^{y}_{0[c]} + \delta^{y}_{0[r]} +
\beta^y_{1}\text{t}_i + \gamma^{y}_{1[c]}\text{t}_i + \delta^{y}_{1[r]}\text{t}_i  \\

i_{i[c][r]} &\sim 
\text{Beta}(\mu^i_{i[c][r]}, \phi^i) \\

\mu^i_{i[c][r]} &= \text{logit}(
\beta^{i}_{0} + \gamma^{i}_{0[c]} + \delta^{i}_{0[r]} +
\beta^i_{1}\text{t}_i + \gamma^{i}_{1[c]}\text{t}_i + \delta^{i}_{1[r]}\text{t}_i) \\

\left[\begin{array}{c}
\gamma^y_{0[c]} \\ \gamma^y_{1[c]} \\ \gamma^i_{0[c]} \\ \gamma^i_{1[c]}
\end{array}\right] 
&\sim MVN(
\left[\begin{array}{c}
0 \\ 0 \\ 0 \\ 0
\end{array}\right],
\Sigma^c
),

\left[\begin{array}{c}
\delta^y_{0[r]} \\ \delta^y_{1[r]} \\ \delta^i_{0[r]} \\ \delta^i_{1[r]}
\end{array}\right] 
\sim MVN(
\left[\begin{array}{c}
0 \\ 0 \\ 0 \\ 0
\end{array}\right],
\Sigma^r
)
\end{align*}
$$

```{r}
# Define a model of internet proportion over time
bf_int <- bf(
  internet ~ 1 + time + 
    (1 + time |c| country) +
    (1 + time |r| region), 
  family = Beta()
)

# Define models of outcomes
bf_anx <- bf(
  Anxiety ~ 1 + time + sex + age + 
    (1 + time + sex + age |c| country) +
    (1 + time + sex + age |r| region),
  family = gaussian()
)
bf_dep <- bf(
  Depression ~ 1 + time + sex + age + 
    (1 + time + sex + age |c| country) +
    (1 + time + sex + age |r| region),
  family = gaussian()
)
bf_sel <- bf(
  Selfharm ~ 1 + time + sex + age + 
    (1 + time + sex + age |c| country) +
    (1 + time + sex + age |r| region),
  family = gaussian()
)

# Fit models
fit_anx <- brm(
  bf_int + bf_anx + set_rescor(FALSE),
  data = gbd_10,
  file = "output/brm-gbd-time-anxiety",
  chains = 4,
  cores = 4,
  iter = hmc$iter, warmup = hmc$warmup, 
  refresh = hmc$refresh,
  control = list(adapt_delta = hmc$d)
)
fit_dep <- brm(
  bf_int + bf_dep + set_rescor(FALSE),
  data = gbd_10,
  file = "output/brm-gbd-time-depression",
  chains = 4,
  cores = 4,
  iter = hmc$iter, warmup = hmc$warmup, 
  refresh = hmc$refresh,
  control = list(adapt_delta = hmc$d)
)
fit_sel <- brm(
  bf_int + bf_sel + set_rescor(FALSE),
  data = gbd_10,
  file = "output/brm-gbd-time-selfharm",
  chains = 4,
  cores = 4,
  iter = hmc$iter, warmup = hmc$warmup, 
  refresh = hmc$refresh,
  control = list(adapt_delta = hmc$d)
)
fits_brm_time_main <- tibble(
  outcome = c("Anxiety", "Depression", "Selfharm"),
  fit = list(fit_anx, fit_dep, fit_sel)
)
```

Coefficients

```{r}
fits_brm_time_main %>% 
  mutate(
    out = map(
      fit, 
      ~as_draws(.x, variable = "b_", regex = TRUE) %>% 
        summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95)))
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  # filter(str_detect(Parameter, "_time$")) %>% 
  kbl(digits = 3) %>% 
  kable_minimal(full_width = FALSE)
```

Revisit figure of temporal trends with coefficients. Note we back-transform the estimated numbers to rates in 100,000

```{r}
tmp_pars <- fits_brm_time_main %>% 
  mutate(
    out = map2(
      fit, 
      outcome,
      ~hypothesis(
        .x, 
        c(str_glue("{.y}_time = 0")),
        scope = "coef",
        group = "region"
      )$hypothesis
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  # Internet trend is estimated in all models--keep first
  distinct(Group, Hypothesis, .keep_all = TRUE) %>% 
  # Transform back to rates in 100k
  mutate(across(where(is.numeric), ~round(.*1000, 0))) %>% 
  mutate(result = str_glue('**{Estimate}** [{CI.Lower}, {CI.Upper}]')) %>% 
  select(cause = Hypothesis, region = Group, result) %>% 
  mutate(cause = str_sub(cause, 2, -6) %>% str_remove("_time"))

p_vars +
  geom_richtext(
    data = tmp_pars %>% mutate(cause = fct_inorder(str_to_title(cause))),
    aes(x = make_date(2000), y = Inf, label = result),
    size = 2.2, vjust = .9, hjust = 0.1, color = "dodgerblue4",
    family = Font,
    fill = NA, label.color = NA
  )
ggsave(
  "output/Fig-vars-timeseries-estimates.png", 
  device = agg_png,
  height = 2400, width = 3600, res = 300, units = "px"
)
```

A figure of coefficients

```{r}
anx_draws <- spread_draws(
  fit_anx, 
  b_Anxiety_time, r_region__Anxiety[region, term] | region
) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_Anxiety_time) %>% 
  mutate(outcome = "Anxiety")
dep_draws <- spread_draws(
  fit_dep, 
  b_Depression_time, r_region__Depression[region, term] | region
) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_Depression_time) %>% 
  mutate(outcome = "Depression")
sel_draws <- spread_draws(
  fit_sel, 
  b_Selfharm_time, r_region__Selfharm[region, term] | region
) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_Selfharm_time) %>% 
  mutate(outcome = "Selfharm")

p_time_main_coefs <- bind_rows(anx_draws, dep_draws, sel_draws) %>% 
  mutate(across(Africa:Southern.Asia, ~.+Average)) %>% 
  pivot_longer(Average:Southern.Asia, names_to = "region") %>% 
  mutate(region = fct_relevel(factor(region), "Average")) %>% 
  mutate(outcome = factor(outcome)) %>% 
  mutate(is_average = region == "Average") %>% 
  mutate(region = str_replace(region, "\\.", " ")) %>% 
  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
  ggplot(aes(value, region, fill = is_average, alpha = is_average)) +
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
  scale_alpha_manual(values = c(.5, .9)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_x_continuous("Linear trend", breaks = pretty_breaks()) +
  stat_halfeye(
    point_interval = NULL, normalize = "panels"
  ) +
  facet_wrap("outcome", nrow = 1, scales = "free_x") +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "none"
  )
p_time_main_coefs
```

###### Correlations

Calculate country coefficients and show scatterplots

```{r time-correlation-anxiety}
# Function to wrangle draws at multiple levels and create scatterplots + ellipses
draw_scatterplot <- function(fit, beta, r_region, r_country, sd_country, cor_country) {
  # Get average and region-specific slopes
  r_region_draws <- fit %>% 
    spread_draws(
      {{beta}}, 
      b_internet_time,
      {{r_region}}[region, term],
      r_region__internet[region, term]
    ) %>% 
    filter(term == "time") %>% 
    ungroup() %>% 
    # Fix names by replacing dot with line break
    mutate(region = str_replace(region, "\\.", "\n"))

  # Then country
  r_country_draws <- fit %>% 
    spread_draws(
      {{r_country}}[country, term],
      r_country__internet[country, term]
    ) %>% 
    filter(term == "time") %>% 
    ungroup() %>% 
    # Fix names by taking labels from original names
    mutate(
      country = factor(
        country, 
        labels = sort(unique(fit$data$country))
      )
    ) %>% 
    left_join(distinct(gbd, region, country))

  # Calculate country coefficients
  country_coefs <- left_join(r_country_draws, r_region_draws) %>% 
    mutate(
      internet = b_internet_time + r_region__internet + r_country__internet,
      outcome = {{beta}} + {{r_region}} + {{r_country}}
    ) %>% 
    group_by(country, region) %>% 
    median_qi(internet, outcome)

  # Create country ellipse data
  country_ellipse <- spread_draws(
    fit,
    {{beta}}, 
    b_internet_time,
    {{sd_country}},
    sd_country__internet_time,
    {{cor_country}}, 
    ndraws = 100
  ) %>% 
    rename(
      cor = {{cor_country}}, 
      sd_outcome = {{sd_country}},
      sd_i = sd_country__internet_time,
      b_outcome = {{beta}},
      b_i = b_internet_time
    ) %>% 
    mutate(
      e = pmap(
        list(cor, sd_outcome, sd_i, b_outcome, b_i), 
        function(cor, sd_a, sd_i, b_a, b_i) 
          ellipse(
            cor, 
            scale = c(sd_i, sd_outcome), 
            centre = c(b_i, b_outcome), 
            level = .90
          ) %>% 
          as_tibble()
      )
    ) %>% 
    unnest(e)

  # Correlation
  country_cor_result <- spread_draws(fit, {{cor_country}}) %>% 
    median_qi(.width = .90) %>% 
    mutate(across(where(is.numeric), ~round(., 2))) %>%
    {str_glue("{.[,1]} [{.[,2]}, {.[,3]}]")}

  # Plot
  country_coefs %>% 
    ggplot(aes(internet, outcome)) +
    geom_path(
      data = country_ellipse,
      aes(x = x, y = y), 
      alpha = .2, size = .1, col = "dodgerblue1"
    ) +
    geom_vline(xintercept = 0, lty = 2, size = .2) +
    geom_hline(yintercept = 0, lty = 2, size = .2) +
    geom_point(col = "dodgerblue1", size = 1, alpha = .5) +
    scale_x_continuous(
      "Internet trend",
      breaks = pretty_breaks()
    ) +
    scale_y_continuous(
      breaks = pretty_breaks()
    ) +
    annotate(
      "text",
      x = Inf, y = Inf, label = country_cor_result,
      size = 4, vjust = 1.5, hjust = 1.05, color = "dodgerblue4",
      family = Font
    )
}
```

```{r}
p_cor_country_anx <- draw_scatterplot(
  fit_anx, 
  b_Anxiety_time, 
  r_region__Anxiety, 
  r_country__Anxiety,
  sd_country__Anxiety_time,
  cor_country__internet_time__Anxiety_time
) + labs(y = "Anxiety trend")
p_cor_country_dep <- draw_scatterplot(
  fit_dep, 
  b_Depression_time, 
  r_region__Depression, 
  r_country__Depression,
  sd_country__Depression_time,
  cor_country__internet_time__Depression_time
) + labs(y = "Depression trend")
p_cor_country_sel <- draw_scatterplot(
  fit_sel, 
  b_Selfharm_time, 
  r_region__Selfharm, 
  r_country__Selfharm,
  sd_country__Selfharm_time,
  cor_country__internet_time__Selfharm_time
) + labs(y = "Self-harm trend")
```

```{r}
p_time_main_correlations <- (p_cor_country_anx |
  p_cor_country_dep |
  p_cor_country_sel) &
  # Transform to rate in 100k
  scale_y_continuous(labels = function(x) x*1000)

(wrap_elements(grid::textGrob('Negative experiences\nTBD')) |
    wrap_elements(grid::textGrob('Positive experiences\nTBD')) |
    wrap_elements(grid::textGrob('Life satisfaction\nTBD'))) /
  p_time_main_correlations

p_time_main_coefs /
  p_time_main_correlations
```

```{r time-correlation-depression}
# Get average and region
r_region_depression <- fit_dep %>% 
  spread_draws(
    b_Depression_time, 
    b_internet_time,
    r_region__Depression[region, term],
    r_region__internet[region, term]
  ) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  # Fix names by replacing dot with line break
  mutate(region = str_replace(region, "\\.", "\n"))

# Then country
r_country_depression <- fit_dep %>% 
  spread_draws(
    r_country__Depression[country, term],
    r_country__internet[country, term]
  ) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  # Fix names by taking labels from original names
  mutate(
    country = factor(
      country, 
      labels = sort(unique(fit_dep$data$country))
    )
  ) %>% 
  left_join(distinct(gbd, region, country))

# Calculate country coefficients
country_depression <- left_join(r_country_depression, r_region_depression) %>% 
  mutate(
    internet = b_internet_time + r_region__internet + r_country__internet,
    depression = b_Depression_time + r_region__Depression + r_country__Depression
  ) %>% 
  group_by(country, region) %>% 
  median_qi(internet, depression)

country_depression_ellipse <- spread_draws(
  fit_dep,
  b_Depression_time, b_internet_time,
  cor_country__internet_time__Depression_time, 
  ndraws = 100
) %>% 
  mutate(
    e = pmap(
      list(
        x = cor_country__internet_time__Depression_time, 
        y = b_internet_time, 
        z = b_Depression_time
      ), 
      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
        as_tibble()
    )
  ) %>% 
  unnest(e)

region_depression_ellipse <- spread_draws(
  fit_dep,
  b_Depression_time, b_internet_time,
  cor_region__internet_time__Depression_time, 
  ndraws = 100
) %>% 
  mutate(
    e = pmap(
      list(
        x = cor_region__internet_time__Depression_time, 
        y = b_internet_time, 
        z = b_Depression_time
      ), 
      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
        as_tibble()
    )
  ) %>% 
  unnest(e)

country_depression_cor <- fit_dep %>%
  as_draws_df(
    variable = c(
      "cor_country__internet_time__Depression_time",
      "cor_region__internet_time__Depression_time"
    ),
    regex = TRUE
  ) %>% 
  as_tibble()
country_depression_result <- country_depression_cor %>%   
  summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95))) %>% 
  mutate(across(where(is.numeric), ~round(., 2))) %>% 
  mutate(result = str_glue("{`50%`} [{`5%`}, {`95%`}]"))

p_cor_country_dep <- country_depression %>% 
  ggplot(aes(internet, depression)) +
  # geom_path(
  #   data = region_depression_ellipse, 
  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue4"
  # ) +
  # geom_path(
  #   data = country_depression_ellipse, 
  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue1"
  # ) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  geom_hline(yintercept = 0, lty = 2, size = .2) +
  geom_point(col = "dodgerblue1", size = 1, alpha = .75) +
  scale_x_continuous(
    "Linear internet trend",
    breaks = pretty_breaks()
  ) +
  scale_y_continuous(
    "Linear depression trend",
    breaks = pretty_breaks()
  ) +
  geom_richtext(
    data = country_depression_result %>% 
      filter(variable == "cor_country__internet_time__Depression_time"),
    aes(x = -Inf, y = Inf, label = result),
    size = 3, vjust = 1, hjust = -0.1, color = "dodgerblue4",
    family = Font,
    fill = NA, label.color = NA
  ) +
  theme(aspect.ratio = 1)
```

```{r time-correlation-selfharm}
# Get average and region
r_region_selfharm <- fit_sel %>% 
  spread_draws(
    b_Selfharm_time, 
    b_internet_time,
    r_region__Selfharm[region, term],
    r_region__internet[region, term]
  ) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  # Fix names by replacing dot with line break
  mutate(region = str_replace(region, "\\.", "\n"))

# Then country
r_country_selfharm <- fit_sel %>% 
  spread_draws(
    r_country__Selfharm[country, term],
    r_country__internet[country, term]
  ) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  # Fix names by taking labels from original names
  mutate(
    country = factor(
      country, 
      labels = sort(unique(fit_sel$data$country))
    )
  ) %>% 
  left_join(distinct(gbd, region, country))

# Calculate country coefficients
country_selfharm <- left_join(r_country_selfharm, r_region_selfharm) %>% 
  mutate(
    internet = b_internet_time + r_region__internet + r_country__internet,
    selfharm = b_Selfharm_time + r_region__Selfharm + r_country__Selfharm
  ) %>% 
  group_by(country, region) %>% 
  median_qi(internet, selfharm)

country_selfharm_ellipse <- spread_draws(
  fit_sel,
  b_Selfharm_time, b_internet_time,
  cor_country__internet_time__Selfharm_time, 
  ndraws = 100
) %>% 
  mutate(
    e = pmap(
      list(
        x = cor_country__internet_time__Selfharm_time, 
        y = b_internet_time, 
        z = b_Selfharm_time
      ), 
      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
        as_tibble()
    )
  ) %>% 
  unnest(e)

region_selfharm_ellipse <- spread_draws(
  fit_sel,
  b_Selfharm_time, b_internet_time,
  cor_region__internet_time__Selfharm_time, 
  ndraws = 100
) %>% 
  mutate(
    e = pmap(
      list(
        x = cor_region__internet_time__Selfharm_time, 
        y = b_internet_time, 
        z = b_Selfharm_time
      ), 
      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
        as_tibble()
    )
  ) %>% 
  unnest(e)

country_selfharm_cor <- fit_sel %>%
  as_draws_df(
    variable = c(
      "cor_country__internet_time__Selfharm_time",
      "cor_region__internet_time__Selfharm_time"
    ),
    regex = TRUE
  ) %>% 
  as_tibble()
country_selfharm_result <- country_selfharm_cor %>%   
  summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95))) %>% 
  mutate(across(where(is.numeric), ~round(., 2))) %>% 
  mutate(result = str_glue("{`50%`} [{`5%`}, {`95%`}]"))

p_cor_country_sel <- country_selfharm %>% 
  ggplot(aes(internet, selfharm)) +
  # geom_path(
  #   data = region_selfharm_ellipse, 
  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue4"
  # ) +
  # geom_path(
  #   data = country_selfharm_ellipse, 
  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue1"
  # ) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  geom_hline(yintercept = 0, lty = 2, size = .2) +
  geom_point(col = "dodgerblue1", size = 1, alpha = .75) +
  scale_x_continuous(
    "Linear internet trend",
    breaks = pretty_breaks()
  ) +
  scale_y_continuous(
    "Linear selfharm trend",
    breaks = pretty_breaks()
  ) +
  geom_richtext(
    data = country_selfharm_result %>% 
      filter(variable == "cor_country__internet_time__Selfharm_time"),
    aes(x = -Inf, y = Inf, label = result),
    size = 3, vjust = 1, hjust = -0.1, color = "dodgerblue4",
    family = Font,
    fill = NA, label.color = NA
  ) +
  theme(aspect.ratio = 1)
```

```{r}
p_cor_country_anx + theme(axis.title.x = element_blank()) | 
  p_cor_country_dep | 
  p_cor_country_sel + theme(axis.title.x = element_blank())
```

##### Time: Interactions

```{r}
# Define models of outcomes
bf_anx <- bf(
  Anxiety ~ 1 + time * sex + time * age + 
    (1 + time * sex + time * age |c| country) +
    (1 + time * sex + time * age |r| region),
  family = gaussian()
)
bf_dep <- bf(
  Depression ~ 1 + time + sex + age + 
    (1 + time * sex + time * age |c| country) +
    (1 + time * sex + time * age |r| region),
  family = gaussian()
)
bf_sel <- bf(
  Selfharm ~ 1 + time + sex + age + 
    (1 + time * sex + time * age |c| country) +
    (1 + time * sex + time * age |r| region),
  family = gaussian()
)

# Fit models
fit_anx <- brm(
  bf_int + bf_anx + set_rescor(FALSE),
  data = gbd_10,
  file = "output/brm-gbd-time-anxiety-int2",
  chains = 4,
  cores = 4,
  iter = hmc$iter, warmup = hmc$warmup, 
  refresh = hmc$refresh,
  control = list(adapt_delta = hmc$d)
)
fit_dep <- brm(
  bf_int + bf_dep + set_rescor(FALSE),
  data = gbd_10,
  file = "output/brm-gbd-time-depression-int2",
  chains = 4,
  cores = 4,
  iter = hmc$iter, warmup = hmc$warmup, 
  refresh = hmc$refresh,
  control = list(adapt_delta = hmc$d)
)
fit_sel <- brm(
  bf_int + bf_sel + set_rescor(FALSE),
  data = gbd_10,
  file = "output/brm-gbd-time-selfharm-int2",
  chains = 4,
  cores = 4,
  iter = hmc$iter, warmup = hmc$warmup, 
  refresh = hmc$refresh,
  control = list(adapt_delta = hmc$d)
)
fits_brm_time_interactions <- tibble(
  outcome = c("Anxiety", "Depression", "Selfharm"),
  fit = list(fit_anx, fit_dep, fit_sel)
)
```

Coefficients

```{r}
fits_brm_time_interactions %>% 
  mutate(
    out = map(
      fit, 
      ~as_draws(.x, variable = "b_", regex = TRUE) %>% 
        summarise_draws(quantile, rhat, .args = list(probs = c(.05, .5, .95)))
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  # filter(str_detect(Parameter, "_time$")) %>% 
  kbl(digits = 2) %>% 
  kable_minimal(full_width = FALSE)
```

Model comparison using waic shows that interactive model is favored across the board.

```{r eval = FALSE}
waics <- left_join(
  rename(fits_brm_time_main, fit_main = fit),
  rename(fits_brm_time_interactions, fit_intr = fit)
) %>% 
  mutate(waic = map2(fit_main, fit_intr, ~waic(.x, .y)))
waics$waic[[3]]
```

Show main effects

```{r}
# Fixed effects parameters
fixed_effects <- fits_brm_time_interactions %>% 
  mutate(out = map(fit, ~tidy(., conf.int = TRUE))) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  standardize_names() %>% 
  as_tibble() %>% 
  filter(
    Effects == "fixed", 
    Parameter != "(Intercept)"
  ) 
# Fixed effects per demographic
fixed_effects_demographics <- fits_brm_time_interactions %>% 
  mutate(
    out = map2(
      fit, outcome,
      ~emtrends(
        .x, 
        var = "time", 
        by = c("sex", "age"), 
        resp = .y
      ) %>% 
        parameters() %>% 
        as.data.frame()
    )
  )
fixed_effects_demographics %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  standardize_names() %>% 
  as_tibble() %>% 
  mutate(Parameter = str_glue("{sex}\n({age})"))

```{r}
library(modelbased)
x <- parameters(fits_brm$fit[[1]], test = "pd", effects = "random", group_level = TRUE, keep = "time_Intercept")
tmp <- fits_brm %>% 
  mutate(
    # Average effect
    avg = map2(
      fit, 
      Outcome, 
      ~hypothesis(.x, str_glue("{.y}_time = 0"))
    ),
    # By country effect
    by_country = map2(
      fit, 
      Outcome, 
      ~hypothesis(
        .x, str_glue("{.y}_time = 0"), 
        scope = "coef", group = "country"
      )
    ),
    # By region effect
    by_region = map2(
      fit, 
      Outcome, 
      ~hypothesis(
        .x, str_glue("{.y}_time = 0"), 
        scope = "coef", group = "region"
      )
    )
  ) %>% 
  select(-fit)

tmp %>% 
  select(Outcome, avg) %>% 
  mutate(avg = map(avg, ))

tmp$by_region[[1]] %>% str

h <- paste(
  c("valAnxiety_Time", "valDepression_Time", "valSelfharm_Time"), 
  "= 0"
)

# Prepare average samples
time_avg <- hypothesis(fit_gbd_time, h)
time_avg_samples <- time_avg$samples
names(time_avg_samples) <- time_avg$hypothesis$Hypothesis
time_avg_samples <- time_avg_samples %>% 
  pivot_longer(everything(), names_to = "Parameter") %>% 
  mutate(region = "Average")

# Prepare region samples
time_region <- hypothesis(fit_gbd_time, h, scope = "coef", group = "region")
time_region_samples <- time_region$samples
names(time_region_samples) <- paste(
  time_region$hypothesis$Hypothesis, 
  time_region$hypothesis$Group, sep = ":"
)
time_region_samples <- time_region_samples %>% 
  pivot_longer(everything(), names_to = "Parameter") %>% 
  separate(Parameter, c("Parameter", "region"), sep = ":")

# Prepare country point estimates
time_country <- hypothesis(fit_gbd_time, h, scope = "coef", group = "country")
time_country_hypothesis <- time_country$hypothesis %>% 
  rename(country = Group, Parameter = Hypothesis)
time_country_hypothesis <- left_join(
  time_country_hypothesis, 
  distinct(fit_gbd_time$data, country, region)
)

time_sum <- bind_rows(
  time_region$hypothesis,
  time_avg$hypothesis %>% mutate(Group = "Average")
) %>% 
  as_tibble() %>% 
  rename(region = Group, Parameter = Hypothesis)

bind_rows(
  time_region_samples,
  time_avg_samples
) %>% 
  mutate(region = fct_relevel(region, "Average")) %>% 
  mutate(Average = region == "Average") %>% 
  ggplot(aes(value/10, region)) +
  scale_y_discrete(
    expand = expansion(c(0.025, 0.075)),
    labels = function(x) ifelse(x == "Average", "**Average**", x)
  ) +
  scale_x_continuous(
    "Estimated yearly change",
    breaks = pretty_breaks(5)
  ) +
  scale_alpha_manual(values = c(.5, 1)) +
  geom_vline(xintercept = 0, size = .2, alpha = .25) +
  stat_eye(
    side = "top",
    aes(col = region, fill = region, alpha = Average),
    point_interval = NULL,
    normalize = "panels", 
    height = .75
  ) +
  geom_pointrangeh(
    data = time_sum,
    aes(x = Estimate/10, xmin = CI.Lower/10, xmax = CI.Upper/10),
    size = .3, fatten = 1.4
  ) +
  geom_point(
    data = time_country_hypothesis,
    aes(col = region, x = Estimate/10), 
    size = .5,
    alpha = .25,
    position = position_nudge(y = -.05)
  ) +
  facet_wrap(
    "Parameter", ncol = 3, scales = "free_x",
    labeller = as_labeller(
      function(x) str_extract(x, "Anxiety|Depression|Selfharm"))
  ) +
  theme(
    axis.text.y = element_markdown(),
    legend.position = "none",
    axis.title.y = element_blank()
  )
ggsave(
  "output/Fig-brm-time-forest.png", 
  device = agg_png,
  height = 1200, width = 3200, res = 300, units = "px"
)
```

>>>>

This script implements the 3-way interactive time model with lme4.

Takes several hours.

@@

```{r fit-gbd-time-lme4}
# run in parallel in background jobs using job()
# recommended to conduct this in interactive mode (rstudio)
file_path <- "output/lme4-gbd-time.rds"
if (!file.exists(file_path)) {
  library(job)
  job({fit_anx <- lmer(
    Anxiety ~ 1 + time * sex * age + 
      (1 + time * sex * age | region) +
      (1 + time * sex * age | country),
    data = gbd_wide
  )}, title = "Anxiety time (lmer)")
  job({fit_dep <- lmer(
    Depression ~ 1 + time * sex * age + 
      (1 + time * sex * age | region) +
      (1 + time * sex * age | country),
    data = gbd_wide
  )}, title = "Depression time (lmer)")
  job({fit_sel <- lmer(
    Selfharm ~ 1 + time * sex * age + 
      (1 + time * sex * age | region) +
      (1 + time * sex * age | country),
    data = gbd_wide
  )}, title = "Self harm time (lmer)")
  fits_lmer <- distinct(gbd, cause) %>% 
    mutate(fit = list(fit_anx, fit_dep, fit_sel))
  write_rds(fits_lmer, file_path)
} else {fits_lmer <- read_rds(file_path)}
```

@@
